%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Full-Stack Software Engineer - Coursemology} % Job title
    {AICET (AI Centre for Educational Technologies) - NUS} % Organization
    {Singapore} % Location
    {Jan. 2023 - Present} % Date(s)
    {
      \begin{cvitems}
        \item {\textbf{Integrated an LLM-powered third-party API to develop an interactive feedback system}, enabling students to ask programming-related questions and receive tailored responses, projected to reduce direct instructor or teaching assistant support requests by 10-20\%.}
        \item {\textbf{Led the integration of Coursemology (a Learning Management System) with Koditsu (an online coding assessment platform)} by developing and implementing solutions from Coursemology's side. Currently supporting a pilot course with 30 students, this integration provides a tailored exam environment for programming challenges and is designed to scale for broader adoption across future courses and larger student cohorts.}
        \item {\textbf{Led Coursemology's backend upgrade from Rails 6.0 to 7.0}, modernizing core dependencies to enhance compatibility, security, and maintainability. The upgrade ensured a smooth transition with minimal disruptions while improving performance, scalability, and developer productivity.}
        \item {\textbf{Designed and deployed a polymorphic real‑time autosave mechanism to handle multiple answer types}, ensuring seamless progress saving for tens of thousands of active students and enhancing data reliability.}
      \end{cvitems}
    }
    {\textbf{Skills/Technologies used: React Typescript, Redux, Ruby on Rails, Sidekiq, PostgreSQL, UI/UX Design, AWS}}

%---------------------------------------------------------
  \cventry
    {Software Engineer (Machine Learning) - Shopping Guide Team} % Job title
    {Shopee Online Private Limited} % Organization
    {Singapore} % Location
    {Sep. 2019 - Sep. 2022} % Date(s)
    {
      \begin{cvitems}
        \item {\textbf{Implemented Swing Algorithm (a graph-based heuristic algorithm based on users' past behavior and keywords' statistical data)}, increasing keyword recommendation click rates by 20\% across 8 markets.}
        \item {\textbf{Contributed to developing a Personalized Deep Learning model to rank the generated list of recommended keywords}, achieving over 80\% AUC in training and validation.}
        \item {\textbf{Extracted keyword and user features using data engineering}, enhancing model training and improving team efficiency.}
      \end{cvitems}
    }
    {\textbf{Skills/Technologies used: Python, Go, Scala, Tensorflow, Deep Learning, SparkSQL}}

%---------------------------------------------------------
\end{cventries}
